---
title: "Homework 2"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Experiment Protocol Analysis

**Possible Protocols**  

*PP1*  
Roll die once, if $X = 6$, then conclude the die is unfair. If $X != 6$, then conclude the die is fair.

With such a small sample, the probability that we would determine what is actually a fair die to be unfair is $1/6$. Conversely, if the die were unfair, the probability that we would deem it to be fair is $ < 5/6$. Given that the unfair die is weighted to roll a 6 more than 1/6 times, the numbers 1-5 would be rolled less than 5/6 times. Depending on the weightedness of the die, that probability could even be zero.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
