---
title: "Homework 2"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Experiment Protocol Analysis

**Possible Protocols**  

*PP1*  
Roll die once, if $X = 6$, then conclude the die is unfair. If $X = 1, 2, 3, 4, 5$, then conclude the die is fair.

With such a small sample, the probability that we would determine what is actually a fair die to be unfair is $1/6$. Conversely, if the die were unfair, the probability that we would deem it to be fair is ( < 5/6). Given that the unfair die is weighted to roll a 6 more than 1/6 times, the numbers 1 to 5 would be rolled less than 5/6 times. Depending on the weightedness of the die, that probability could even be zero.

*PP2*  
Roll die 30 times.

Decision Rule: The expected number of outcomes where (x = 6) is the probability of rolling a 6 times the number of trials.
1/6 * 30 = 5. If we observe 6 approximately 5 times, we can conclude that the die is fair.

Were we to roll a fair die, we would expect to observe a 6 on 5 occasions. We can approach the problem using a binomial distribution - we either observe a 6, classified as a success, or we do not observe a 6, a failure. We would expect to roll a 6 on 5 occasions 19.2% of the time. Rolling one more or one less 6 would occur 16% and 18.5% of the time, respectively.

Our sample size and probability of success is large enough to let us approximate the binomial using the normal distribution. Accounting for the continuity correction, the probability of rolling a 6 on 4 or 6 occasions is 17.2%, each. Rolling a 6 from 4 to 6 times would occur 37.6% of the time. I conclude that it is not particularly unusual to roll one more or one less 6.

Below is a table of probabilities from the binomial distribution:

```{r PP2, echo=FALSE}
read.csv("PP2outcomes.csv", header = TRUE, strip.white = TRUE, fill = FALSE, nrow = 7)[,1:2]
```

As with one more or less, rolling a 6 on 2 more or 2 less occasions sits within 1 standard deviation of the mean, so it is not particularly unusual. We would expect approximately 68% of our samples to produce a 6 on 3, 4, 5, 6 or 7 occasions. Rolling a 6 three more or less times is less common - a 6 occurring twice or 8 times are approximately 1.47 standard deviations from the mean of 5.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
